\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Propuesta de Grupo}

### 2016-03-05 article.tex
Añadido porcentaje de trabajo realizado por cada miembro del grupo.

\author{
\large
\textsc{Alberto Amigo Alonso}\\[2mm] % Your name
\textsc{Sergio Delgado Álvarez}\\[2mm] % Your name
\textsc{Sergio García Prado}\\[2mm] % Your name
\textsc{Oscar Fernández Angulo}\\[2mm] % Your name
\normalsize Universidad de Valladolid \\ % Your institution
\vspace{-5mm}
}
\date{}

>>>>

\author{
\large
\textsc{Alberto Amigo Alonso\textsubscript{25\%}}\\[2mm] % Your name
\textsc{Sergio Delgado Álvarez\textsubscript{25\%}}\\[2mm] % Your name
\textsc{Sergio García Prado\textsubscript{25\%}}\\[2mm] % Your name
\textsc{Oscar Fernández Angulo\textsubscript{25\%}}\\[2mm] % Your name
\normalsize Universidad de Valladolid \\ % Your institution
\vspace{-5mm}
}
\date{}
